Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition.

### 2015-06-28 papers/data_paper/datapaper.tex
cisiamo

\title{Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.}

@@

%\clearpage
\input{table_sample.tex}
%\noindent
\input{table_observations.tex}

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs), 
listed in Table \ref{tab:obs}.
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be %``enhanced Level 1 products'', or
corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It appears as a decaying trail of pixels, repeating every fourth column.
``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

@@

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
Such deficits were first noted and researched by \cite{kingminkowski1966}.
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
\citep{dullograham2014cores,rusli2013}.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies using this alternative method when 
no high resolution image was available.

@@

\section{Results}
\label{sec:res}
For each galaxy, after we identified its various components and built a model accordingly, 
we simultaneously performed a set of four 1D fits.
All four fits use a Moffat-convolved model.
Two fits use the major-axis surface brightness profile and the remaining two use the equivalent-axis surface brightness profile. 
For each of these pairs, we use a logarithmically sampled surface brightness profile 
and a linearly sampled surface brightness profile. 
Because our fitting routine intentionally does not employ an error weighting scheme on the data points that constitute the surface brightness profile, 
a fit to a logarithmically sampled profile puts more weight on the inner region of the galaxy 
and poorly constrains the outskirts.
On the other hand, a fit to a linearly sampled surface brightness profile equally treats inner and outer regions, 
but is more susceptible to sky-background subtraction issues. \\ 
We found that the fits are, in general, more sensitive to the choice of the initial parameters 
when using logarithmically sampled profiles than linearly sampled profiles. 
In addition, a visual examination of the residuals revealed that the quality of the fit within one galaxy effective radius 
is superior when tighter constraints are put on the galaxy outskirts.
In other words, the better quality of the residuals led us to prefer the fits that use linearly sampled surface brightness profiles,
although the results were ususally very similar,as might be expected. \\
Among the initial sample of 75 galaxies, we did not attempt to model 3 galaxies: M32, NGC 4486A and the Circinus Galaxy. 
The first two... {\bf AL: can you write a short sentence about these 2 galaxies, that have uncertain morphology,
because they have been stripped, blah blah, maybe put one reference? please and thank you.}
The Circinus Galaxy lies at only 4 degrees from the Galactic Plane, 
therefore its image mosaic is contaminated by a large number of foreground stars.
Of the remaining 72 galaxies, 
we obtained satisfactory 1D decompositions for 66, 
whereas the models of 6 galaxies were judged not reliable and were thus excluded. 
We also performed reliable 2D decompositions for 31 galaxies. \\
A galaxy-by-galaxy comparison between our best-fit models and those from the previous literature 
helped identify the optimal decompositions and past problems. 
We compared our best-fit models with those of \cite{grahamdriver2007}, \cite{sani2011}, \cite{beifiori2012}, 
\cite{vika2012} and \cite{lasker2014data}. 
We also considered the best-fit models of \cite{laurikainen2010} and \cite{rusli2013} because,   
although they did not specifically deal with black hole -- galaxy scaling relations, 
their galaxy samples significantly overlap with ours. \\
%In Section \ref{sec:indgal} we discuss individual cases, explaining the discrepancies between different decompositions. \\
Table \ref{tab:fitres} lists the results from both the 1D and 2D fits.

@@

\begin{itemize}
\item One-dimensional and two-dimensional techniques of galaxy decomposition return the same results when applied to the same galaxy.
However, in our practical experience, two-dimensional decompositions {\bf HOW DO YOU WRITE THIS IN ENGLISH?? fail twice as much as one-dimensional ones}, 
either because the fit does not converge or because the result is unphysical. 
A strong limitation of two-dimensional codes is their inability to accommodate the radial gradients of ellipticity and position angle 
often observed in galaxy bulges.
\item We found the interpretation of one-dimensional residual surface brightness profiles easier than that of two-dimensional residual images. 
A correct interpretation of the residuals is fundamental to determine the optimal model for a galaxy.
\item A one-dimensional isophotal analysis was extremely helpful and sometimes even necessary to accurately identify galaxy components.
\item Given the level of detail to which each galaxy decomposition was performed, 
we believe that our analysis cannot be reproduced by current automatic routines. 
\item The uncertainties associated with the bulge best-fit parameters are dominated by systematic errors (e.g.~incorrect sky subtraction, 
inaccurate masking of contaminating sources, erroneous choice of model components), and only marginally affected by random errors. 
For this reason, we developed a method to estimate the uncertainties on the best-fit parameters that takes into account systematic errors.
\end{itemize}

@@

{\bf Lasker's conclusions are: bulge+disk decompositions are not enough, we do better by adding bars, spiral arms and stuff (really?? what a surprising conclusion);
we modelled the envelope of 5 galaxies; we observed central light deficits in 9 ellipticals; total magnitudes are independent from details of modelling (no, really?)
and bulge magnitudes are 0.36 mag fainter when additional components (other than bulge and disk) are modelled.  }

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M104.
  }
  \end{center}
  \end{figure}

@@

  ok

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 1316.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 1316.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-bar + 2 G-r + G-n & $21.5$  &  $2.0$ \\
  T.W. 1D eq.  & S-bul + e-d + F-bar + 2 G-r + G-n & $15.9$  &  $1.8$ \\
  %T.W. 2D	&  & $$  & $$  &  $$ \\
  \hline
  S+11      & S-bul + e-d + G-n & $93.0$  &  $5.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n1316}
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 5128.
  NGC 5128 is a merging system. }
  \end{center}
  \end{figure}

>>>>

\title{Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition.}

@@

%\clearpage
\input{table_sample.tex}
%\noindent
%\input{table_observations.tex}

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs). 
%listed in Table \ref{tab:obs}.
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be %``enhanced Level 1 products'', or
corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It appears as a decaying trail of pixels, repeating every fourth column.
``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

@@

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
Such deficits were first noted and researched by \cite{kingminkowski1966}.
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
\citep{dullograham2014cores,rusli2013}.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2015},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies using this alternative method when 
no high resolution image was available.

@@

\section{Results}
\label{sec:res}
For each galaxy, after we identified its various components and built a model accordingly, 
we simultaneously performed a set of four 1D fits.
All four fits use a Moffat-convolved model.
Two fits use the major-axis surface brightness profile and the remaining two use the equivalent-axis surface brightness profile. 
For each of these pairs, we use a logarithmically sampled surface brightness profile 
and a linearly sampled surface brightness profile. 
Because our fitting routine intentionally does not employ an error weighting scheme on the data points that constitute the surface brightness profile, 
a fit to a logarithmically sampled profile puts more weight on the inner region of the galaxy 
and poorly constrains the outskirts.
On the other hand, a fit to a linearly sampled surface brightness profile equally treats inner and outer regions, 
but is more susceptible to sky-background subtraction issues. \\ 
We found that the fits are, in general, more sensitive to the choice of the initial parameters 
when using logarithmically sampled profiles than linearly sampled profiles. 
In addition, a visual examination of the residuals revealed that the quality of the fit within one galaxy effective radius 
is superior when tighter constraints are put on the galaxy outskirts.
In other words, the better quality of the residuals led us to prefer the fits that use linearly sampled surface brightness profiles,
although the results were ususally very similar,as might be expected. \\
Among the initial sample of 75 galaxies, we did not attempt to model 3 galaxies: M32, NGC 4486A and the Circinus Galaxy. 
The first two have been stripped by their massive companions, and thus have uncertain morphology. 
The Circinus Galaxy lies at only 4 degrees from the Galactic Plane, 
therefore its image mosaic is contaminated by a large number of foreground stars.
Of the remaining 72 galaxies, 
we obtained satisfactory 1D decompositions for 66, 
whereas the models of 6 galaxies were judged not reliable and were thus excluded. 
We also performed reliable 2D decompositions for 31 galaxies. \\
A galaxy-by-galaxy comparison between our best-fit models and those from the previous literature 
helped identify the optimal decompositions and past problems. 
We compared our best-fit models with those of \cite{grahamdriver2007}, \cite{sani2011}, \cite{beifiori2012}, 
\cite{vika2012} and \cite{lasker2014data}. 
We also considered the best-fit models of \cite{laurikainen2010} and \cite{rusli2013} because,   
although they did not specifically deal with black hole -- galaxy scaling relations, 
their galaxy samples significantly overlap with ours. \\
%In Section \ref{sec:indgal} we discuss individual cases, explaining the discrepancies between different decompositions. \\
Table \ref{tab:fitres} lists the results from both the 1D and 2D fits.

@@

\begin{itemize}
\item One-dimensional and two-dimensional techniques of galaxy decomposition return the same results when applied to the same galaxy.
However, in our practical experience, the failure rate of two-dimensional decompositions 
is a factor of two higher than the failure rate of one-dimensional decompositions,  
either because the fit does not converge or because the result is unphysical. 
A strong limitation of two-dimensional codes is their inability to accommodate the radial gradients of ellipticity and position angle 
often observed in galaxy bulges.
\item We found the interpretation of one-dimensional residual surface brightness profiles easier than that of two-dimensional residual images. 
A correct interpretation of the residuals is fundamental to determine the optimal model for a galaxy.
\item A one-dimensional isophotal analysis was extremely helpful and sometimes even necessary to accurately identify galaxy components.
\item Given the level of detail to which each galaxy decomposition was performed, 
we believe that our analysis cannot be reproduced by current automatic routines. 
\item The uncertainties associated with the bulge best-fit parameters are dominated by systematic errors (e.g.~incorrect sky subtraction, 
inaccurate masking of contaminating sources, erroneous choice of model components), and only marginally affected by random errors. 
For this reason, we developed a method to estimate the uncertainties on the best-fit parameters that takes into account systematic errors.
\end{itemize}

@@

%{\bf Lasker's conclusions are: bulge+disk decompositions are not enough, we do better by adding bars, spiral arms and stuff (really?? what a surprising conclusion);
%we modelled the envelope of 5 galaxies; we observed central light deficits in 9 ellipticals; total magnitudes are independent from details of modelling (no, really?)
%and bulge magnitudes are 0.36 mag fainter when additional components (other than bulge and disk) are modelled.  }

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M104. 
  M104 is a lenticular/spiral galaxy with a partially depleted core. 
  The data within the innermost $6''.1$ are excluded from the fit, 
  and the most obvious ring of the galaxy is modeled.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 1316. 
  NGC 1316 is a merger. 
  The galaxy is composed of a bulge, an elongated structure that can be identified with a bar, 
  two obvious rings, an outer exponential disk or halo, and a bright nuclear component. }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 1316.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-bar + 2 G-r + G-n & $21.5$  &  $2.0$ \\
  T.W. 1D eq.  & S-bul + e-d + F-bar + 2 G-r + G-n & $15.9$  &  $1.8$ \\
  %T.W. 2D	&  & $$  & $$  &  $$ \\
  \hline
  S+11      & S-bul + e-d + G-n & $93.0$  &  $5.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n1316}
  \tablecomments{
  S+11 overestimated the bulge effective radius and S\'ersic index because their model does not take into account the bar.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 5128.
  NGC 5128 is a merging system. 
  The data within $50'' \lesssim R_{\rm maj} \lesssim 200''$ is excluded from the fit.}
  \end{center}
  \end{figure}
